Constraints on Cosmic-Ray Particle Populations, Magnetic Fields, and Dark Matter from VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS

### 2011-09-09 ms.tex
small changes to text

\subsection{Simplified analytical model}
To complement the simulation-inspired analysis and to facilitate comparison with earlier analytical
work, we repeat the data analysis with a simplified analytical model that assumes a power-law CR
spectrum and a constant relative CR pressure, i.e., we adopt the {\em isobaric model of CRs}. To be
independent of additional assumptions and in line with earlier work in the literature, we do not
impose a low-momentum cutoff on the CR distribution function, i.e., we adopt $q=0$. Since a priori,
the CR spectral index is unconstrained, we vary it within plausible ranges of
$2.1<\alpha_{\rmn{p}}<2.5$. This spectral range is compatible with the radio spectral index of the
giant radio halo of Coma after accounting for the spectral steepening at frequencies
$\nu\sim5~\rmn{GHz}$ due to the Sunyaev-Zel'dovich effect
\citep{article:PfrommerEnsslin:2004b}\footnote{Assuming a magnetic field of 1 $\mu$G, the CR protons
  responsible for the GHz radio emitting electrons have an energy of $\sim100$ GeV and are $\sim$ 20
  times less energetic than those CR protons responsible for 200-GeV gamma-ray emission.}. Table
\ref{table:constraints} shows the resulting constraints on $X_\CR$. The VERITAS flux upper limits
strongly depend on $\alpha$ due to the comparably large lever arm from GeV energies (that dominate
the CR pressure) to TeV-energies. The limits within 0.2$^{\circ}$ are most constraining yielding
limits on $X_\CR$ between 0.048 and 0.43 (for $\alpha$ varying between 2.1 and 2.5), with a
constraint of $X_\CR<0.1$ for $\alpha=2.3$ (close to the spectral index predicted by the simulations
around 220 GeV). This limit is more constraining by 50\% in comparison to the model derived from
simulations, which gives $X_\CR<0.15$. This difference is explained by the concave curvature of the
simulated spectrum which accumulates additional pressure toward GeV energies in comparison to a pure
power-law spectrum of $\alpha=2.3$.

>>>>

\subsection{Simplified analytical model}
To complement the simulation-inspired analysis and to facilitate comparison with earlier analytical work, we repeat the data analysis with a simplified analytical model that assumes a power-law CR spectrum and a constant relative CR pressure, i.e., we adopt the {\em isobaric model of CRs} following the approach of \citet{2004A&A...413...17P}. To be independent of additional assumptions and in line with earlier work in the literature, we do not impose a low-momentum cutoff on the CR distribution function, i.e., we adopt $q=0$. Since a priori, the CR spectral index is unconstrained, we vary it within plausible ranges of $2.1<\alpha_{\rmn{p}}<2.5$. This spectral range is compatible with the radio spectral index of the giant radio halo of Coma after accounting for the spectral steepening at frequencies $\nu\sim5~\rmn{GHz}$ due to the Sunyaev-Zel'dovich effect \citep{article:PfrommerEnsslin:2004b}\footnote{Assuming a magnetic field of 1 $\mu$G, the CR protons responsible for the GHz radio emitting electrons have an energy of $\sim100$ GeV and are $\sim$ 20 times less energetic than those CR protons responsible for 200-GeV gamma-ray emission.}. Table \ref{table:constraints} shows the resulting constraints on $X_\CR$. The VERITAS flux upper limits strongly depend on $\alpha$ due to the comparably large lever arm from GeV energies (that dominate the CR pressure) to TeV-energies. The limits within 0.2$^{\circ}$ are most constraining yielding limits on $X_\CR$ between 0.048 and 0.43 (for $\alpha$ varying between 2.1 and 2.5), with a constraint of $X_\CR<0.1$ for $\alpha=2.3$ (close to the spectral index predicted by the simulations around 220 GeV). This limit is more constraining by 50\% in comparison to the model derived from simulations, which gives $X_\CR<0.15$. This difference is explained by the concave curvature of the simulated spectrum which accumulates additional pressure toward GeV energies in comparison to a pure power-law spectrum of $\alpha=2.3$.
